\begin{enumerate}[i.-]
\item \textit{Bufferbloat: Dark Buffers in the Internet}\\
	Author: Jim Gettys, Kathleen Nichols\\
	Published: Queue vol. 9, no. 11, November 29, 2011\\
	Comment: This publication, Jim Gettys presents the reason and why he begun to research about this phenomenon. Also he present some fundamentals of how this phenomenon is generated and some results of his research.
\item \textit{BufferBloat: What's Wrong with the Internet?}\\
	Published: Queue vol. 9, no. 12, December 7, 2011\\
	Comment: A discussion with Vint Cerf, Van Jacobson, Nick Weaver, and Jim Gettys about the \textit{BufferBloat} phenomenon, how Gettys got motivated by Cerf to explore his home network to find the problem of ``why it was so slow", the explanation of what this phenomenon its and some other technical information related with this topic.
\item \textit{jg's Ramblings}\\
	Author: Jim Gettys\\
	\url{http://gettys.wordpress.com/}\\
	Comment: This is Gettys' personal blog. Here he write about his intrest topic. Lately he is been ``\textit{posting}" about \textit{BufferBloat}, the way he did the first experiments, how he realize that was a problem and some other technical information about this phenomenon.
\item \textit{Understanding bufferbloat and the network buffer arms race}\\
	\url{http://arstechnica.com/tech-policy/news/2011/01/}\\
	\url{understanding-bufferbloat-and-the-network-buffer-arms-race.ars}\\
	Comment: A less technical explanation of this phenomenon, the causes and how it affect the performance of a network. It makes reference mostly to the job that Gettys has done lately.
\item \textit{BufferBloat}\\
	\url{http://www.bufferbloat.net/}\\
	Comment: This is a website where you can find project related with the performance, testing and general information related with this phenomenon. Also you can find several mailing lists, git repositories, and people here that are attempting to address the Bufferbloat issues at various levels.
\end{enumerate}
