According to the reports published by SUBTEL to the first half of 2013,
\textit{12.8} per 100 inhabitants have access to broadband
Internet\cite{OCDE}.  This steady growth is largely due to the emergence of
new applications such as streaming video and music, online gaming and
intensive applications bandwidth.

Since not long ago, the links had a much more limited access than they are
today, but with the evolution of electronics and telecommunications, these
speeds have increased dramatically. At this point, the role of each component
of this communication becomes important. With this level of data flowing
through the network, it is important to maintain controlled congestion that
might occur; This is the task of the routers.

It is important to remember that the traffic in a network is inherently
bursty, so the role of the buffers in the router is to smooth the flow of
traffic. Without any buffering, to allocate the bandwidth evenly would be
impossible. But there are some problems with current algorithms; they use
tail-drop based queue management that has two big drawbacks: 1.- lockout 2.-
full queue that impact with a high queue delay.

With actual low prices in hardware makes more easy the access to cheap memory,
and with the ``more is better'' mentality have led to the inflation and
proliferation of buffers everywhere\cite{NicholsJacobsonCQD}. When a router
joins two network with different bandwidths, each packet is squeezed down in
bandwidth, it must stretch out in time since its size stays constant. When
this queue starts to growth, more and more memory is deployed leading to
massive standing queues. It turns out that this is a recipe for Bufferbloat.
Evidence of Bufferbloat has been accumulating over the past decade, but its
existence has not yet become a widespread cause for concern.

Bufferbloat creates large delays but no improvement in throughput. It is not a
phenomenon treated by queueing or traffic theory, which unfortunately, results
in it being almost universally misclassified as congestion. The \textit{\gls{Bufferbloat}}
problem, making the window match the pipe size, is hard to address. Window
sizes are chosen by senders while queues manifest at bottleneck gateways.


As mentioned by Jim Gettys and Kathleen Nichols;
\textit{Today's networks are suffering from unnecessary latency and poor
system performance. The culprit is Bufferbloat, the existence of excessively
large and frequently full buffers inside the network. Large buffers have been
inserted all over the Internet without sufficient thought or testing. They
damage or defeat the fundamental congestion-avoidance algorithms of the
Internet's most common transport protocol. Long delays from Bufferbloat are
frequently attributed incorrectly to network congestion, and this
misinterpretation of the problem leads to the wrong solutions being
proposed}\cite{GettysNichols}.

The objective of this thesis work consists of checking the effects of
Bufferbloat phenomenon, test the impact that it has in over different networks
and to generate possible solutions. To accomplish this, it first required to
address the following general objectives:

\begin{itemize}
	\item To explain the \textit{Bufferbloat} phenomenon, and explain the impact that it could have over latency and \gls{Throughput}(related to \gls{System Throughput}) in Internet.
	\item To detect the presence by empirical measure of the latency and throughput in a TCP/IP Network.
	\item To propose possible solutions in the implementation of a network where the existence of excessively large and frequently buffers are detected
\end{itemize}

In order to archive theses objectives is needed:

\begin{itemize}
\item To develop appropriate test to be able to prove the existence of \textit{Bufferbloat}
\item To test and differentiate the possible cause of the excessive latency and diminish of throughput in a TCP/IP LAN and proof how much is generated by \textit{Bufferbloat} or by a miss-configuration
\item To propose a possible configuration of the TCP parameters in a Linux based machine or an algorithm that can help to minimize the phenomenon.
\end{itemize}

In Chapter 2, it will be explained the basis on which TCP was developed and
the fundamentals for the current operation of the Internet. The conservation
principle upon which are based all communication protocols will be explained.
Also, explain each of the four phases consisting TCP.

In Chapter 3 we will review one of the most important components for the
communication and the main place where the packages are stored: the Routers.
It will be analyzed how their queues have a destructive size for
communication, why they are stalled at full capacity and cause a excessive
latency. Also consider how the appropriate size to hold the buffers that are
located in a router is defined.

Chapter 4 presented a technique developed to deal more efficiently with
actively congestion that could generate not only on endpoints but also on
routers. This technique is Active queue management (AQM). How the first
algorithms, such as RED and BLUE, were implemented and mention
CODEL which aims to solve the Bufferbloat phenomenon; This failures points,
in both TCP and AQM, are synthesized and analyze. All this will be presented in
Chapter 5.

Chapter 6 aims to define the methodology and tools that will be used to
perform each of the tests to determine the existence and the effects of
Bufferbloat. Each test is defined by its propose starting with some general
tests to check the behavior and sanity of the network and moving to a more
user-related effects of the Bufferbloat. All the tools used are Open Source
projects available for all commercial operative systems. In Chapter 7 the
results of all tests are presented, leading to the conclusions of this work in
chapter 8.
