\documentclass[letter, 11pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage{amsfonts, amsmath, amsthm, amssymb}
\usepackage[dvips]{graphicx}
\usepackage{url}
\usepackage[top=3cm,bottom=3cm,left=3.5cm,right=3.5cm,footskip=1.5cm,headheight=1.5cm,headsep=.5cm,textheight=3cm]{geometry}
\usepackage{listings}
\usepackage{color}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{hyperref}
%% to use the warpfigure capability
\usepackage{wrapfig}
%% Double spacing
\usepackage{setspace}
%% To use appendix
\usepackage[title,titletoc,toc]{appendix}
% Justify caption text
\usepackage[justification=centering]{caption}
%two tabular same table
\usepackage{tabularx}
\usepackage{caption}
\usepackage{subcaption}
%modificar margenes
\usepackage{anysize} 
%Glosario
\usepackage[nonumberlist]{glossaries}

%%%%%%%%%%%%%%%%%%%%%%
%Estilo del documento%
%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{fancyplain}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Fancyheadings. Top y Bottom del documento%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Recuerde que en este documento la portada del documento no posee
% numeracion, pero de igual manera llamaremos a esa primera pagina la numero
% 1, y la que viene la dos. Esto es para tener una idea de las que
% llamaremos pares e impares	
\lhead{} %Parte superior izquierda
\rhead{\bf \it UTFSM, Casa Central} %Parte superior derecha
\lfoot{JSCO} %Parte inferior izquierda.
\cfoot{} %Parte inferior central
\rfoot{\bf \it Page \thepage} %Parte inferior derecha
\renewcommand{\footrulewidth}{0.4pt} %Linea de separacion inferior
\renewcommand{\thefootnote}{\roman{footnote}}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem*{theoremnon}{Theorem}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition} % definition numbers are dependent on theorem numbers
\newtheorem{exmp}[thm]{Example} % same for example numbers

\setcounter{secnumdepth}{5} %activate subsubsubsection = paragraph

\marginsize{3,5cm}{2,5cm}{3cm}{3,5cm} 

\makeglossaries
%
\newglossaryentry{BDP}{name={Bandwidth Delay Product (BDP)},description={An amount of data measured in
bits. It is equivalent to the maximum amount of data on the network circuit at
any given time. Commonly measured by the RTT*bandwidth.
}}
%
\newglossaryentry{BW}{name={Bottleneck bandwidth}, description={The smallest bandwidth along the path.
Packets cannot arrive at the destination any faster than it takes to
send a packet at the bottleneck rate	}}
%
\newglossaryentry{Bufferbloat}{name={Bufferbloat},description={Refers to excess buffering inside a network,
resulting in high latency and reduced throughput.}}
%
\newglossaryentry{cwin}{name={Congestion Window (cwin)},description={One of the factors that
determines the bytes that can be outstanding at any time. It
prevents the overload of the link with too much traffic. The size is
calculated by estimating the congestion between the two places.}}

\newglossaryentry{ECN}{name={Explicit Congestion Notification (ECN)}, description={Defined in RFC 3168. ECN allows end-to-end notification of network congestion without dropping packets. ECN is an optional feature that may be used between two ECN-enabled endpoints when the underlying network infrastructure also supports it.}}

\newglossaryentry{LFN}{name={Long Fat Network (LFN)},description={A network with a large bandwidth-
delay product. Often $>> 10^5$ bits (12500 bits). }}

\newglossaryentry{mss}{name={Maximum Segment Size (mss)},description={Largest amount of data (in
octets) that a communication device can receive in a single TCP segment
(single IP datagram). Established by pass on the syn packet.}}
%
\newglossaryentry{MTU}{name={Maximum Transmission Unit (MTU)},description={MTU of a
layer is the largest protocol data unit that the layer can pass onwards. In
ethernet the MTU is 1500 bytes.}}
%
\newglossaryentry{ssthrsh}{name={Slow start threshold (ssthrsh)},description={It determine whether the
TCP should do Slow Start or Congestion Avoidance. It is initialized to a large
value, and after a congestion is signaled, cwin is divided in half and ssthrsh
is set to cwin.}}
%
\newglossaryentry{sojourn}{name={Sojourn},description={A period of time when you stay in place as a
traveler or guest. Example: Sojourned for a month at the mountains.}}
%
\newglossaryentry{System Throughput}{name={System Throughput},description={Corresponds to the fastest rate at which
the count of packets transmitted to the destination by the network is equal to
the number of packets sent into the network.}}
%
\newglossaryentry{Throughput}{name={Throughput},description={Measure of the efficiency of a network expressed
as the data(bits or packets) transfer rate of useful and  non-redundant
information. It depends on factors such as bandwidth, line congestion, error
correction, etc. }}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tema de las referencias %
\bibliographystyle{acm}
%%%%%%%%%%%%%%%%%%%%%%%%%%

\include{portada}

\newpage
\printglossary

\newpage
\tableofcontents
\listoffigures
\listoftables

\newpage

\doublespacing
%section Intro
\section{Introduction}
\input{src/intro}
%end intro

\newpage

%section TCP
\section{The Transport Control Protocol}
\input{src/tcp/tcp}

\subsection{Fundamentals of TCP}
\input{src/tcp/fundamentals}

\subsection{TCP's Phases }
\input{src/tcp/phases}
%end TCP

\newpage

%section Buffers 
\section{Router's Buffers effects}
\input{src/buff/buffs}
\subsection{Full Buffers}
\input{src/buff/full_buffs}
\subsection{High Latency}
\input{src/buff/latency}
\subsection{Sizing Router's Buffers}
\input{src/buff/sizing}
%end Buffers

\newpage

%section AQM
\section{Active Queue Management}
\input{src/aqm/aqm}
\subsection{RED}
\input{src/aqm/red}
\subsection{BLUE}
\input{src/aqm/blue}
\subsection{CoDel}
\input{src/aqm/codel}
%end AQM

\newpage

%Flaws
\section{Hidden Flaws and Bufferbloat}
\input{src/tcp/flaws}
%end Flaws

\newpage

%section Test
\section{Experimental Work}
\input{src/test/experimental}

\subsection{The Test Setup}
\input{src/test/setup}

\subsection{Tools Definition}
\input{src/test/tools}

\subsection{Test Description}
\input{src/test/description}
	
%end section Test
\newpage
%section Results
\section{Results}
\input{src/results/results}

\subsection{Speed test}
\input{src/results/speed}

\subsection{Netalyzr test}
\input{src/results/netalyzr}

\subsection{Iperf test}
\input{src/results/iperf }

\subsection{Benchmark test}
\input{src/results/benchmark }

\subsection{Smokeping Test}
\input{src/results/smokeping }

\subsection{Summarising Results}
\input{src/results/all}
%end section Test
\newpage
%section Test
\section{Conclusions and Further Work}
\input{src/conclusions}
%end section Conclusions
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%incluyo referencias
\bibliography{references,rfc}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendix}
\section{Speed Test Details results}\label{app:bwmeasures}
\input{src/app/bwmeasures}
\newpage
\section{Page Benchmark results}\label{app:pbmeasures}
\input{src/app/benchmark_app}
\end{appendix}

\end{document}
